\documentclass[a4paper,twoside,11pt]{article}
\usepackage{enumerate, a4wide,graphicx,fancyhdr,amsmath,amssymb, amsfonts, listings, titlesec}

%----------------------- Macros and Definitions --------------------------

\setlength\headheight{20pt}
\addtolength\topmargin{-10pt}
\addtolength\footskip{20pt}

\newcommand{\N}{\mathbb{N}}
\newcommand{\ch}{\mathcal{CH}}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\newcommand{\solution}[1]{\noindent{\bf Solution to Exercise #1:}}

\fancypagestyle{plain}{%
\fancyhf{}
\fancyhead[LO,RE]{\sffamily\bfseries\large Technische Universiteit Eindhoven}
\fancyhead[RO,LE]{\sffamily\bfseries\large 2IO23 DBL Specification and Game}
\fancyfoot[LO,RE]{\sffamily\bfseries\large department of mathematics and computer science}
\fancyfoot[RO,LE]{\sffamily\bfseries\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[RO,LE]{\sffamily\bfseries\large Technische Universiteit Eindhoven}
\fancyhead[LO,RE]{\sffamily\bfseries\large 2IO23 DBL Specification and Game}
\fancyfoot[LO,RE]{\sffamily\bfseries\large department of mathematics and computer science}
\fancyfoot[RO,LE]{\sffamily\bfseries\thepage}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{0pt}

\titleformat{\section}
  {\normalfont\Large\bfseries\centering}{\thesection}{1em}{}
\titleformat{\subsection}
  {\normalfont\large\bfseries\centering}{\thesubsection}{1em}{}

%-------------------------------- Title ----------------------------------

\title{\vspace{-\baselineskip}\sffamily\bfseries Meeting Scheduler}
\author{Author, nummer}

\date{\today}

%--------------------------------- Text ----------------------------------

\begin{document}

\section{Message Sequence Charts}
\subsection{Connect}
The following MSC describes the connecting of a client with a server.

\subsection{SendReceiveServer}
The following MSC describes the sending of data from a client to a server, where the server then processes the data and sends a reply.

\subsection{SendReceivePeers}
The following MSC describes the sending of data from one client to another client.

\subsection{GetHighScoreData}
The following MSC describes the retrieval of retrieving the high score data which is stored on the server.

\subsection{Create match}
The following MSC describes the creation of a match.\\
The creation of the match follows several steps:
\begin{enumerate}
\item Connecting to the server (2-5).
\item Loading the lobby list (6-7).
\item Lobby creation (8-10).
\item Having enough players that are ready (11-12).
\item Starting the game (13).
\end{enumerate}

\subsection{Join match}
The following MSC describes the creation of a match.\\
The joining of the match follows several steps:
\begin{enumerate}
\item Connecting to the server (2-5).
\item Loading the lobby list (6-7).
\item Joining a lobby (8-10).
\item Having enough players that are ready (11-12).
\item Starting the game (13).
\end{enumerate}

\subsection{Edit options}
The following MSC describes the editing of the options relating to the game.\\
The editing of the options has two steps:
\begin{enumerate}
\item Getting the options (1-3).
\item While the play did not press close, the play can edit any amount of options (which are instantly saved when edited).
\end{enumerate}

\subsection{Check how to play}
The following MSC describes the checking of the how to play of the game.\\

\subsection{Check highscores}
The following MSC describes the checking of the highscores of the game.\\
The checking of the highscores has two steps:
\begin{enumerate}
\item Getting the highscore data (ref GetHighScoreData, section TODO.4)
\item Display the highscore data.
\end{enumerate}

\subsection{Quit game}
The following MSC describes the quiting of the game.\\

\subsection{Move}
The following MSC describes the move action in the game.\\
Movement in the game is described in two steps:
\begin{enumerate}
\item Notifying other peers in the game of the move (1-3).
\item All peers update their respective players (4-5).
\end{enumerate}

\subsection{Pick up flag}
The following MSC describes the pick up flag action in the game.\\
The picking up of a flag can be divided in two steps:
\begin{enumerate}
\item Picking up the flag, and notifying other peers of it (1-3)
\item Showing the fact that the player has picked up flag to all other players (4).
\end{enumerate}

\subsection{Activate block}
The following MSC describes the activate block action in the game.\\
The activation of a block can be divided in two steps:
\begin{enumerate}
\item Colliding with the block (1)
\item Stating the fact that there has been a collision with a block to other peers (2-3).
\item Updating the effect of the player activating the block on all peers (4).
\end{enumerate}

\subsection{Fire weapon}
The following MSC describes firing in the game.\\
The firing divided in two steps:
\begin{enumerate}
\item The player firing (1)
\item Notifying all other peers of the fact that player fired (2-3).
\item Update player health in response to the firing (4-5).
\end{enumerate}

\subsection{Deliver flag}
The following MSC describes delivering a flag in the game.\\
Delivering a flag can be divided in several steps:
\begin{enumerate}
\item The player moves (ref Move, section TODO.11).
\item The player is in the drop zone (1).
\item Notify all other peers that the player moved into the drop zone (2-3).
\item Open the doors of the base in which drop zone the player is (4-5).
\item The flag is delivered (6).
\item Notifying all the other peers of the player delivering a flag (7-8).
\item Either the flag is delivered and points are given to the player (9-10) or the base is claimed, and a point given to the player (11-12).  
\end{enumerate}

\end{document}
