\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\section{Client}
The Client has 2 variables:
\begin{enumerate}
\item[\textbf{userName}] The username associated with this client.
\item[\textbf{peers}] A list of the IP addresses of the clients this client currently has a peer to peer connection with.
\end{enumerate}
The Client has 3 methods:
\begin{enumerate}
\item[\textbf{Connect}] Connects the client to a peer/server at the given IP.
\item[\textbf{SendMessage}] Sends a message to a connected peer/server.
\item[\textbf{ReceiveMessage}] Receives a message from a connected peer/server.
\end{enumerate}
\section{Server}
The Server has 2 variables:
\begin{enumerate}
\item[\textbf{lobbyIPs}] List of lobbies, where a lobby is a list (of at most length 6) of IP addresses. 
\item[\textbf{readyList}] List inside a list mapped one to one to lobbyIPs. This two dimensional list contains booleans indicating if a player is ready. The player associated with each boolean is the owner of the IP address the boolean is mapped to.
\end{enumerate}
The Server has 4 methods:
\begin{enumerate}
\item[\textbf{Listen}] Listens to connection requests from clients and connects to the clients.
\item[\textbf{WaitRequest}] Waits for messages from connected clients.
\item[\textbf{HandleRequest}] Processes messages from connected clients and sends messages back if required.
\item[\textbf{Start}] Broadcasts the IP addresses in a lobby to the clients in the lobby as soon as the requirements to start the game are satisfied, and empties the lobby.
\end{enumerate}
\end{document}
